Kolmogorov-Smirnov

### 2020-04-09 ks/ks.Rmd
Use 'write.csv' instead of 'sink', as it renders better
Watermark artificial data

```{r}
sink("table_1.latex")
  xtable::print.xtable(
    xtable::xtable(
      df,
      caption = paste0("Percentage of epitopes overlapping \nwith transmembrane helix"),
      digits = 3
    ),
    include.rownames = FALSE
  )
sink()
```

@@

```{r}
ggplot(df, aes(x = haplotype, y = f, fill = proteome)) + 
  scale_fill_manual(values = c("human" = "#ffffff", "covid" = "#cccccc")) +
  geom_col(position = position_dodge(), color = "#000000") + xlab("HLA haplotype") + 
  ylab("% epitopes overlapping \nwith transmembrane helix") +
  geom_hline(yintercept = mean(f_human), lty = "dashed") +
  geom_hline(yintercept = mean(f_covid), lty = "dotted") +
  labs(
    title = "SIMULATED DATA!",
    caption = paste0(
      "Dashed line: average in humans: ", formatC(mean(f_human), digits = 2),". ",
      "Dotted line: average in COVID-19: ", formatC(mean(f_covid), digits = 2),"."  
    )
  ) + ggsave("fig_1.png", width = 7, height = 7)
```

>>>>

```{r}
write.csv(df, "table_1.csv", row.names = FALSE)
```

@@

```{r}
ggplot(df, aes(x = haplotype, y = f, fill = proteome)) + 
  scale_fill_manual(values = c("human" = "#ffffff", "covid" = "#cccccc")) +
  geom_col(position = position_dodge(), color = "#000000") + xlab("HLA haplotype") + 
  ylab("% epitopes overlapping \nwith transmembrane helix") +
  geom_hline(yintercept = mean(f_human), lty = "dashed") +
  geom_hline(yintercept = mean(f_covid), lty = "dotted") +
  labs(
    caption = paste0(
      "Dashed line: average in humans: ", formatC(mean(f_human), digits = 2),". ",
      "Dotted line: average in COVID-19: ", formatC(mean(f_covid), digits = 2),"."  
    )
  ) + ggsave("fig_1.png", width = 7, height = 7)
```
